Story Cloze Task: UW NLP System

### 2017-02-16 docs/shared_task_paper_camera_ready.tex
Camera ready style changes

\documentclass[11pt]{article}
\usepackage{eacl2017}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym,xcolor}
\usepackage{multirow}

@@

\newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
\newcommand{\roy}[1]{{\color{orange}\textsc{[#1 --rs]}}}
\newcommand{\royb}[2]{{\color{red}{\sout{#1}}}{\color{green}{#2}}}
\newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}
\newcommand{\yc}[1]{{\color{bblue}\{\textit{#1}\}$_{yc}$}}
\newcommand{\nascomment}[1]{\textcolor{blue}{[\textsc{#1 --nas}]}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\com}[1]{}
\definecolor{forestgreen}{rgb}{0.13, 0.55, 0.13}

@@

\author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.5cm}Maarten Sap$^1$ \And \hspace{3cm}Ioannis Konstas$^1$ \And \\
  $^1$Computer Science \& Engineering, University of Washington,
  Seattle, WA 98195, USA \\
  $^2$Allen Institute for Artificial Intelligence, Seattle, WA 98103, USA \\
    {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\
    \And \hspace{-2cm}Leila Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A.~Smith$^1$ \\
  }

\date{}

@@

We add the following classification features to capture style differences between the two endings. 
These features are computed on the story endings alone ({\it right} or {\it wrong}), and do not consider, either at train nor at test time, the first four (shared) sentences of each story.
\begin{itemize}
\item\textit{\textbf{Length}.} The number of words in the sentence.
\item\textit{\textbf{Word $n$-grams.}} We use sequences of 1--5
  words. Following \newcite{Tsur:2010} and \newcite{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
Specifically, we replace content words, which are often low frequency, with their part-of-speech tags (Nouns, Verbs, Adjectives, and Adverbs).
\item\textit{\textbf{Character $n$-grams.}} Character $n$-grams are useful features in the detection of author style \cite{Stamatatos:2009} or language identification \cite{lui2011cross}.
We use character 4-grams.
\end{itemize}

@@

For computing the style features, the story cloze task doesn't have a training corpus for the {\it right} and {\it wrong} endings.
Therefore, we use the development set as our training set, holding out 10\% for development
(3,366 training endings, 374 for development). We keep the story cloze test set as is (3,742 endings).
We add a \textsc{start} symbol at the beginning
of each sentence.\footnote{Virtually all sentences end with a period
  or an exclamation mark, so we do not add a \textsc{stop} symbol.} 
 We keep $n$-gram (character or word) features that occur at least five times in the training set.
All stylistic feature values are normalized to [0, 1] \nascomment{the
  range [0, 1] or the two values \{0, 1\}?}
For the part-of-speech features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
The total number of features used by our system is 7,651.

@@

\bibliography{acl2017}
\bibliographystyle{eacl2017}

>>>>

\documentclass[11pt]{article}
\usepackage{authblk}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym,xcolor}
\usepackage{multirow}
\usepackage{eacl2017}

@@

\newcommand{\ms}[1]{{\color{cyan}\{\textit{#1}\}$_{ms}$}}
\newcommand{\roy}[1]{{\color{orange}\textsc{[#1 --rs]}}}
\newcommand{\royb}[2]{{\color{red}{\sout{#1}}}{\color{green}{#2}}}
\newcommand{\royc}[3]{\royb{#1}{#2}\roy{#3}}
\newcommand{\yc}[1]{{\color{bblue}\{\textit{#1}\}$_{yc}$}}
\newcommand{\nascomment}[1]{\textcolor{blue}{[\textsc{#1 --nas}]}}
\newcommand{\tabref}[1]{Table~\ref{#1}}
\newcommand{\com}[1]{}
\newcommand{\resolved}[1]{}
\definecolor{forestgreen}{rgb}{0.13, 0.55, 0.13}

@@

\com{
\author{\hspace{2cm}Roy Schwartz$^{1,2}$ \And \hspace{2.5cm}Maarten Sap$^1$ \And \hspace{3cm}Ioannis Konstas$^1$ \And \\
  $^1$Computer Science \& Engineering, University of Washington,
  Seattle, WA 98195, USA \\
  $^2$Allen Institute for Artificial Intelligence, Seattle, WA 98103, USA \\
    {\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}  \\
    \And \hspace{-2cm}Leila Zilles$^1$ \And \hspace{-2.5cm}Yejin Choi$^1$ \And \hspace{-2.5cm}Noah A.~Smith$^1$ \\
  }
  }

\author[1,2]{\bf Roy Schwartz}
\author[1]{\bf Maarten Sap}
\author[1]{\bf Ioannis Konstas}
\author[1]{\bf Leila Zilles}
\author[1]{\bf Yejin Choi}
\author[1]{\bf Noah A.~Smith}
\affil[1]{Computer Science \& Engineering, University of Washington, Seattle, WA 98195, USA}
\affil[2]{Allen Institute for Artificial Intelligence, Seattle, WA 98103, USA}
\affil[  ]{\tt \{roysch,msap,ikonstas,lzilles,yejin,nasmith\}@cs.washington.edu}
\date{}

@@

We add the following classification features to capture style differences between the two endings. 
These features are computed on the story endings alone ({\it right} or {\it wrong}), and do not consider, either at train or at test time, the first four (shared) sentences of each story.
\begin{itemize}
\item\textit{\textbf{Length}.} The number of words in the sentence.
\item\textit{\textbf{Word $n$-grams.}} We use sequences of 1--5
  words. Following \newcite{Tsur:2010} and \newcite{Schwartz:2013}, we distinguish between high frequency and low frequency words. 
Specifically, we replace content words, which are often low frequency, with their part-of-speech tags (Nouns, Verbs, Adjectives, and Adverbs).
\item\textit{\textbf{Character $n$-grams.}} Character $n$-grams are useful features in the detection of author style \cite{Stamatatos:2009} or language identification \cite{lui2011cross}.
We use character 4-grams.
\end{itemize}

@@

For computing the style features, the story cloze task doesn't have a training corpus for the {\it right} and {\it wrong} endings.
Therefore, we use the development set as our training set, holding out 10\% for development
(3,366 training endings, 374 for development). We keep the story cloze test set as is (3,742 endings).
We add a \textsc{start} symbol at the beginning
of each sentence.\footnote{Virtually all sentences end with a period
  or an exclamation mark, so we do not add a \textsc{stop} symbol.} 
 We keep $n$-gram (character or word) features that occur at least five times in the training set.
All stylistic feature values are normalized to the range [0, 1] \resolved{\nascomment{the
  range [0, 1] or the two values \{0, 1\}?}}
For the part-of-speech features, we tag all endings with the Spacy POS tagger.\footnote{\url{spacy.io/}}
The total number of features used by our system is 7,651.

@@

\bibliography{eacl2017}
\bibliographystyle{eacl2017}
